Seshadri constants of curve configurations on surfaces

### 2024-03-20 sc-curve-config.tex
Changes by Krishna-Almost Final-1

By \cite[Example 3.5]{JP}, the above question has a negative answer for the Hesse arrangement of conics 
in $\mathbb{P}^2$. However it is open for line arrangements in $\mathbb{P}^2$. 
It is interesting to study the situations in which it is true on arbitrary surfaces. Our main theorem answers this question positively under an additional nefness condition.

@@

	For star arrangements, the base constant is exactly equal to $C_1^2(d-1)$. We answer the above question positively for some arrangements  in the following  corollaries

@@

 \begin{proof}
 The proof is immediate from Theorem \ref{main-theorem}.    
 \end{proof}

@@

The proof of Theorem \ref{main-theorem} shows that for arrangements
satisfying Assumption \ref{star1}, we have the following lower and upper bounds for the Seshadri constants.

@@

Note that the hypotheses of Theorem \ref{main-theorem} hold here. 
 For any reduced and irreducible curve $D$ which is not in $\mathcal{C}$, we showed in the proof of Theorem \ref{main-theorem}
that the Seshadri ratio is at least $\frac{L\cdot C_1}{C_1^2(d-1)}$. 
So we obtain $\frac{L\cdot C_1}{C_1^2(d-1)} \le \varepsilon(X, L,{\rm Sing}(\mathcal{C}))$.

>>>>

By \cite[Example 3.5]{JP}, the above question has a negative answer for the Hesse arrangement of conics 
in $\mathbb{P}^2$. However it is open for line arrangements in $\mathbb{P}^2$. 
It is interesting to study the situations in which it is true on arbitrary surfaces. Our main theorem below answers this question positively under an additional nefness condition.

@@

	For star arrangements, the base constant is exactly equal to $C_1^2(d-1)$. We answer the above question positively for some arrangements below.

@@

 \begin{proof}
Under the given hypotheses, we have $b_i = C_1^2(d-1)$  and $L\cdot C_i = L\cdot L_1$
for all $i$. 
The proof is now immediate from Theorem \ref{main-theorem}.    
 \end{proof} This immediately gives the following.

@@

The proof of Theorem \ref{main-theorem} can be modified to show that for arrangements
satisfying Assumption \ref{star1} which are not star arrangements, we still have the following lower and upper bounds for the Seshadri constants.

@@

Let  $D \notin \mathcal{C}$ be 
a reduced and irreducible curve which contains some points of the singular locus $\mathcal{P}$ of $\mathcal{C}$. Essentially following the proof of Theorem \ref{main-theorem}, we can show that 
$$ \frac{L\cdot C_1}{C_1^2(d-1)} \le \frac{L \cdot D}{\sum_{p \in \mathcal{P}} m_{p}(D)}.$$

%$D \notin \mathcal{C}$, we showed in the proof of Theorem \ref{main-theorem} that the Seshadri ratio is at least $\frac{L\cdot C_1}{C_1^2(d-1)}$. 
%So we obtain $\frac{L\cdot C_1}{C_1^2(d-1)} \le \varepsilon(X, L,{\rm Sing}(\mathcal{C}))$.

Indeed, suppose that the above inequality does not hold. 
As in the proof of Theoerem \ref{main-theorem}, B\'ezout's theorem applied to $D$ and $C_1+\dots+C_d$ gives

$$		 D\cdot (C_{1}+ \ldots + C_{d}) \ge  
\frac{2(d-1)(L \cdot D)C_1^2}{L\cdot C_1}.$$

		Now we use the nefness of 
  $\frac{dC_1^2}{(d-1)(L\cdot C_1)}L-C_1$ and obtain a contradiction exactly as in the proof of Theorem \ref{main-theorem}. We omit the details since the argument is identical.
